TODO \thanks{ The original version of this paper is entitled ``Interactive Checks for Coordination Avoidance'' and was published in PVLDB Vol.\ 12. }

### 2020-05-17 doc/sigmod_paper/sections/related_work.tex
More aggressive cutting.
Need to polish now since I hastily chopped a bunch of stuff.

% \textbf{Branch and Merge.}
Bayou~\cite{terry1995managing}, Dynamo~\cite{decandia2007dynamo}, and
TARDiS~\cite{crooks2016tardis} all take a branch and merge approach to
maintaining distributed invariants without coordination. With this approach,
servers execute transactions without any coordination but keep track of the
causal dependencies between transactions. Periodically, two servers merge
states and invoke a user defined merge function to reconcile the divergent
states. This approach does \emph{not} provide any formal guarantees that
invariants are maintained.
% Its correctness depends on the correctness of the
% potentially complex user defined merge functions.

% \textbf{CRDTs.}
CRDTs~\cite{shapiro2011conflict, shapiro2011comprehensive} are distributed
semilattices with inflationary update methods. Due to their algebraic
properties, CRDTs can be replicated with strong eventual consistency without
the need for any coordination. Our definition of distributed objects and our
\invariantconfluence{} system model are inspired directly by the corresponding
definitions and system models in~\cite{shapiro2011conflict}.

@@

\begin{techreport}

  \textbf{Program Analysis in Database Systems.} Using program analysis to
  improve the performance of database systems is not new. For example, it has
  been used to improve the performance of database-backed web
  applications~\cite{cheung2014using, wu2016transaction,
  ramachandra2012program} and used to improve the performance of optimistic
  concurrency control on multi-core machines~\cite{wu2016transaction}. Our work
  on \invariantconfluence{} continues the theme of using program analysis to
  reap the performance benefits gained from understanding program semantics.
\end{techreport}

>>>>

% \textbf{Branch and Merge.}
% Bayou~\cite{terry1995managing}, Dynamo~\cite{decandia2007dynamo}, and
% TARDiS~\cite{crooks2016tardis} all take a branch and merge approach to
% maintaining distributed invariants without coordination.
% With this approach,
% servers execute transactions without any coordination but keep track of the
% causal dependencies between transactions. Periodically, two servers merge
% states and invoke a user defined merge function to reconcile the divergent
% states.
% This approach does \emph{not} provide any formal guarantees that
% invariants are maintained.
% Its correctness depends on the correctness of the
% potentially complex user defined merge functions.

% \textbf{CRDTs.}
% CRDTs~\cite{shapiro2011conflict, shapiro2011comprehensive} are distributed
% semilattices with inflationary update methods. Due to their algebraic
% properties, CRDTs can be replicated with strong eventual consistency without
% the need for any coordination. Our definition of distributed objects and our
% \invariantconfluence{} system model are inspired directly by the corresponding
% definitions and system models in~\cite{shapiro2011conflict}.

@@

### 2020-05-17 doc/sigmod_paper/sections/segmented_invariant_confluence.tex
More aggressive cutting.
Need to polish now since I hastily chopped a bunch of stuff.

\begin{example}\examplelabel{CounreachableExample}
  Let $O = (\ints^3 \times \ints^3, \join)$ be an object that separately keeps positive and negative integer counts (dubbed a
  PN-Counter~\cite{shapiro2011comprehensive}), replicated on three machines.
  Every state $s = $ $(p_1, p_2, p_3),$ $(n_1, n_2, n_3)$ represents the
  integer $(p_1 + p_2 + p_3) - (n_1 + n_2 + n_3)$. To increment or decrement
  the counter, the $i$th server increments $p_i$ or $n_i$ respectively, and
  $\join$ computes an element-wise maximum. Our start state $s_0 = (0, 0, 0),
  (0, 0, 0)$; our set $T$ of transactions consists of increment and decrement;
  and our invariant $I$ is that the value of $s$ is non-negative.

  Applying \algoref{InteractiveDecisionProcedure}, \IsIclosed{} returns false
  with the states $s_1 = (1, 0, 0), (0, 1, 0)$ and $s_2 = (1, 0, 0), (0, 0,
  1)$. Both are reachable, so $O$ is not \sTIconfluent{} and
  \algoref{InteractiveDecisionProcedure} returns false.  The culprit is
  concurrent decrements, which we can forbid in a simple one-segment
  segmentation $\Sigma = (I, T^+)$ where $T^+$ consists only of increment
  transactions. Applying, \algoref{ArbitraryStartInteractiveDecisionProcedure},
  \IsIclosed{} again returns false with the same states $s_1$ and $s_2$. This time,
  however, the user recognizes that the two states are not
  \ticoreachable{T^+}{I} (all modifications of $(n_1, n_2, n_3)$ require global
  coordination, so it is impossible for $s_1$ and $s_2$ to differ on these
  values).
  The user refines $NR$ with the observation that two
  states are coreachable if and only if they have the same values of $n_1, n_2,
  n_3$. After this, \IsIclosed{} and
  \algoref{ArbitraryStartInteractiveDecisionProcedure} return true.
\end{example}

>>>>

% \begin{example}\examplelabel{CounreachableExample}
%   Let $O = (\ints^3 \times \ints^3, \join)$ be an object that separately keeps positive and negative integer counts (dubbed a
%   PN-Counter~\cite{shapiro2011comprehensive}), replicated on three machines.
%   Every state $s = $ $(p_1, p_2, p_3),$ $(n_1, n_2, n_3)$ represents the
%   integer $(p_1 + p_2 + p_3) - (n_1 + n_2 + n_3)$. To increment or decrement
%   the counter, the $i$th server increments $p_i$ or $n_i$ respectively, and
%   $\join$ computes an element-wise maximum. Our start state $s_0 = (0, 0, 0),
%   (0, 0, 0)$; our set $T$ of transactions consists of increment and decrement;
%   and our invariant $I$ is that the value of $s$ is non-negative.
%
%   Applying \algoref{InteractiveDecisionProcedure}, \IsIclosed{} returns false
%   with the states $s_1 = (1, 0, 0), (0, 1, 0)$ and $s_2 = (1, 0, 0), (0, 0,
%   1)$. Both are reachable, so $O$ is not \sTIconfluent{} and
%   \algoref{InteractiveDecisionProcedure} returns false.  The culprit is
%   concurrent decrements, which we can forbid in a simple one-segment
%   segmentation $\Sigma = (I, T^+)$ where $T^+$ consists only of increment
%   transactions. Applying, \algoref{ArbitraryStartInteractiveDecisionProcedure},
%   \IsIclosed{} again returns false with the same states $s_1$ and $s_2$. This time,
%   however, the user recognizes that the two states are not
%   \ticoreachable{T^+}{I} (all modifications of $(n_1, n_2, n_3)$ require global
%   coordination, so it is impossible for $s_1$ and $s_2$ to differ on these
%   values).
%   The user refines $NR$ with the observation that two
%   states are coreachable if and only if they have the same values of $n_1, n_2,
%   n_3$. After this, \IsIclosed{} and
%   \algoref{ArbitraryStartInteractiveDecisionProcedure} return true.
% \end{example}
